### 2025-02-17 paper/paper.tex
Add  multi agent, update metrics.

\begin{itemize}
    \item Without loss of generality, we fix the true state to be $\omega = 0$ hence the optimal action is $a_\omega = 0$.
    \item Signal generation with accuracy $q$:
    \[
        P(s_t = \omega) = q, \quad P(s_t \neq \omega) = 1-q
    \]
    \item The reward function derived in the binary case section:
    \[
        v(a,s) = \frac{q \cdot \mathbf{1}_{\{a = s\}} - (1-q) \cdot \mathbf{1}_{\{a \neq s\}}}{2q-1}
    \]
\end{itemize}

@@

\subsubsection*{Metrics Tracking}
We track three key metrics throughout the learning process:

\begin{itemize}
    \item \textit{Policy}: The proportion of the wrong action in agent's policy, computed as:
    \[
        P(a_t \neq a_\omega) = \frac{1}{t}\sum_{s=1}^t \mathbf{1}_{\{a_s \neq a_\omega\}}
    \]

    \item \textit{Mistake Rate}: The empirical probability of the agent choosing an incorrect action, computed as the running average of mistakes:
    \[
        P(a_t \neq a_\omega) = \frac{1}{t}\sum_{s=1}^t \mathbf{1}_{\{a_s \neq a_\omega\}}
    \]

    \item \textit{Learning Rate}: Following the paper's definition, we compute:
    \[
        r = \liminf_{t \to \infty} -\frac{1}{t} \log P(a_t \neq a_\omega)
    \]
    To approximate this limit, we compute the learning rate over exponentially increasing time windows and take the minimum rate, ensuring we capture the asymptotic behavior.
\end{itemize}
For the binary case with symmetric signals, the theoretical bound on the learning rate is:
\[
    r_{bdd} = -\log(1-q_{bdd}) = -\log(1-(2q-1))
\]
where $q_{bdd} = 2q-1$ is the bound on the probability of choosing the correct action. This provides a benchmark against which we can evaluate the empirical learning rate of our implementation.

\subsubsection*{Experimental Setup}
The implementation is evaluated over a single continuos training run for a signal accuray of $q=0.75$ and $T=10^5$ steps. We track the evolution of the mistake rate, policies and empirical learning rate over time to compare against the theoretical bound. The results are visualized in Figure \ref{fig:single-learning-curves}. The learning curves demonstrate that the agent successfully learns to minimize mistakes and that the learning rate stays below the theoretical learning rate bound, validating the implementation.

@@

@@

@@

\subsubsection*{Experimental Setup}
The implementation is evaluated over a single continuos training run for signal accuries of $q \in \{0.1, 0.9\}$ to test the robustness of learning across informativeness of the signal for both paradigms with $T=10^5$ steps each. We track the evolution of the mistake rate, policies and empirical learning rate over time to compare against the theoretical bound. The results are visualized in Figure \ref{fig:multi-learning-curves-ctde} and \ref{fig:multi-learning-curves-dtde}. The learning curves demonstrate that the agent successfully learns to minimize mistakes and that the learning rate stays below the theoretical learning rate bound, validating the implementation.

@@

\pagebreak

>>>>

\begin{itemize}
    \item Without loss of generality, we fix the true state to be $\omega = 1$ hence the optimal action is $a_\omega = 1$.
    \item Signal generation with accuracy $q$:
    \[
        P(s_t = \omega) = q, \quad P(s_t \neq \omega) = 1-q
    \]
    \item The reward function derived in the binary case section:
    \[
        v(a,s) = \frac{q \cdot \mathbf{1}_{\{a = s\}} - (1-q) \cdot \mathbf{1}_{\{a \neq s\}}}{2q-1}
    \]
\end{itemize}

@@

@@

\subsubsection*{Metrics Tracking}
We track four key metrics throughout the learning process, computed over a sliding window to smooth the learning curves:

\begin{itemize}
    \item \textit{Signals}: The raw signals received by each agent, which helps visualize the information quality available to agents given the signal accuracy $q$.

    \item \textit{Observed Rewards}: The rewards observed by each agent based on the signal-dependent reward function:
    \[
        v(a,s) = \frac{q \cdot \mathbf{1}_{\{a = s\}} - (1-q) \cdot \mathbf{1}_{\{a \neq s\}}}{2q-1}
    \]

    \item \textit{Proportions of True Action}: The proportion of time each agent selects the correct action in their policy, reflecting how well the agents have learned to identify the optimal action.

    \item \textit{Learning Rates}: Approximating the paper's definition:
    \[
        r^{empirical} =  -\frac{1}{t} \log P(a_t \neq a_\omega)
    \]
    This is compared against the theoretical bound for the binary case with symmetric signals:
    \[
        r_{bdd} = 2(2q-1)\log\frac{q}{1-q}
    \]
\end{itemize}

The implementation is evaluated over a single continuos training run for a signal accuray of $q=0.75$ and $T=10^4$ steps. We present the results in Figure \ref{fig:single-learning-curves} with a running average of window size 1000. The learning curves demonstrate that the agent successfully learns to minimize mistakes and that the learning rate stays below the theoretical learning rate bound, validating the implementation. The observed rewards start to oscillate around the true reward level of $1$ just before the 2000th step, which also coincides with the converge of the policy to the optimal action.

@@

In Figure \ref{fig:multi-learning-curves-ctde}, we plot the simulation metrics as running averages of a window of 100 steps. We  observe that for a continuos trainining run with 4 agents, $T= 1000$ steps and $q=0.75$ signal accuracy, all agents successfully learn the true action and that the learning rate stays below the theoretical learning rate bound, validating the implementation.

@@

@@

In Figure \ref{fig:multi-learning-curves-dtde}, we plot the simulation metrics for the DTDE approach, with the same parametrization as before. Just as with CTDE, we see an early converge to true rewards and true actions. The learning rate stays below the theoretical learning rate bound, validating the implementation. However, with both approaches, we noticed divergence from the optimal policy during longer time steps that even take place after what seemed to be a convergence to perfect learning, begging for further investigation. 
\pagebreak
